\chapter{Implementation}

\chapterintro{
  This chapter details a proof-of-concept implementation of Cloud-SAP architecture.
}

\section{Introduction}
Previous chapters detailed requirements that a self-manageable platform oriented toward Quality-of-Service assurance should comply with. Beside this, reference architecture known as Cloud-SAP was introduced. This chapter in turn highlights key elements of a proof-of-concept implementation of Cloud-SAP. Noticeably, our implementation is by all means not exhaustive and merely intends to prove that presented architecture successfully tackles raised challenges. Hence, we implemented only following subset of managers specified by Cloud-SAP:
\begin{itemize}
  \item Autonomic container manager
  \item Autonomic stack manager
  \item Autonomic cloud instance manager
  \item Autonomic cloud federation manager
\end{itemize}

Apart from that, we based analysis solely on threshold model, discarding more advanced techniques using prediction mechanisms.

\section{Overview}
As previous section indicates, key elements of discussed implementation are as follows: autonomic container manager, autonomic stack manager, autonomic cloud instance manager, autonomic cloud federation manager. Taking their role in service deployment into account, we grouped them into auto-scaling and cloud brokerage subsystems. Figure XXX illustrates relation between Cloud-SAP managers and above-mentioned subsystems and figure YYY depicts high level overview of a system.

As one can see, our implementation is composed by following parts:
\begin{asparaenum}
 \item[\textbf{Auto-scaling subsystem}]

 \item[\textbf{Cloud brokerage subsystem}] 
 
 \item[\textbf{Cloud provider}] 
 
 \item[\textbf{Customer}] 
\end{asparaenum}

With those information in mind, we can illustrate overall architecture, components and communication protocols on deployment diagram ZZZ. Successive sections portrays in detail specified elements.

\section{Auto-scaling subsystem}

\section{Cloud brokerage subsystem}

\section{Cloud provider}

\section{Exemplary scenarios}

\subsection{Service deployment}

\subsection{Scaling application}

\subsection{Scaling application across multiple cloud providers}

\section{Summary}

